DNSKEY Management

### 2012-12-07 paper/paper.tex
added a ref

\subsection{Computing power}
DNSSEC does not only require a higher coordination among the three R's, it also increases the strain on the computing infrastructure of a registrar when the size and quantity of the  zones it manages grow: updates to a zone or key rollovers require cryptographic signing operations that are orders of magnitude more expensive than simply updating a DNS record. Even with improvements like incremental signing, the computational requirements are significant and must be considered when a registrar wishes to enable DNSSEC.
%TODO find good ref on this.

>>>>

\subsection{Computing power}
DNSSEC does not only require a higher coordination among the three R's, it also increases the strain on the computing infrastructure of a registrar when the size and quantity of the  zones it manages grow: updates to a zone or key rollovers require cryptographic signing operations that are orders of magnitude more expensive than simply updating a DNS record. Even with improvements like incremental signing~\cite{signMetrics}, the computational requirements are significant and must be considered when a registrar wishes to enable DNSSEC.
%TODO find good ref on this.
